\LARGE{{\bf{Piled up gravitational waves:} \\ \bf{Searching for new signals of $N$naturalness} }}

### 2019-08-02 gwnnDraft02.tex
Change author list

\title{\LARGE{{\bf{Piled up gravitational waves:} \\
\bf{Searching for new signals of $N$naturalness} }}}
\author{{\bf {Paul Smith$\,^{a}$}}}

\affiliation{
$^a$Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada
}

>>>>

\title{\LARGE{{\bf{Piled up gravitational waves:} \\
\bf{Searching for new signals of $N$naturalness} }}}
\author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}

\affiliation{
Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada
}
